Robust positively invariant sets for state dependent and scaled disturbances

### 2015-03-20 draft.tex
Edited section IV - linearised model and derivation of linearisation errors.

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
\Psi^i\mathcal V(\mathcal X_k)\right)}_{=\mathcal S_2}.

@@

$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot y)^T$. We find that an equilibrium
is present when $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$ for any positive position $x_1>0$.
Linearising the nonlinear differential equation $\dot x = f(x,u)$ around $\hat x, \hat u$ we obtain the linear approximation

@@

	\Delta \dot x = \underbrace{\left(\begin{array}{cc}

@@

	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat u)}\Delta x + \underbrace{\left(\begin{array}{c}

@@

	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat u)}\Delta u.

@@

We derive discrete time system dynamics using the explicit Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$,
with the sampling rate $T_s$. Hence we define the system matrix $A = (I+T_s\frac{\partial f}{\partial x}(\hat x,\hat u))$
and the input matrix $B = T_s \frac{\partial f}{\partial u}(\hat x,\hat u)$. 
Notice that using a non-autonomous model does not affect our analysis since we analyse the closed loop system
governed by a linear state feedback controller $u=Kx$. We choose $K$ as the solution of the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$ for a minimised $\gamma^2$, 
see e.g.~\cite{Boyd:94}.
A representation of additive disturbances that act on the state of the linearised model as a result of the linearisation error can be obtained using the mean-value theorem for vector valued functions (e.g.~\cite{Apostol:1974}):

@@

Let $\mathcal X\subset\mathbb R^n$ be open, $g : \mathcal X \rightarrow\mathbb R^m$ continuously differentiable, 
and $x \in\mathcal X, h \in\mathbb R^n$ vectors such that the 
whole line segment $x + th$ remains in $\mathcal X$ for $0 \leq t \leq 1$. Then

@@

Using the Mean Value Theorem~\ref{thm:mean:value:theorem}
and the linearisation for $\Delta x = \hat x + \tilde x$ and $\Delta u = \hat u + \tilde u$ we
get the successor state:

@@

	\Delta x^+ = \underbrace{\tilde f(\hat x, \hat u)}_{\hat x} + \int_0^1\frac{\partial\tilde 
	f}{\partial x}(\hat x + t\tilde x
	,\hat u + t\tilde u)dt\cdot \tilde x +\\
	 \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x
	,\hat u + t\tilde u)dt\cdot \tilde u + A \tilde x + B \tilde u - A \tilde x - B\tilde u\\
	\Leftrightarrow \tilde x^+ = A\tilde x + B \tilde x +\left(
	\int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u + t\tilde u)dt - A
	\right)\tilde x + \\ \left(
	\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B
	\right)\tilde u

@@

Thus for any state $\tilde x=\Delta x - \hat{x}$ we obtain the (exact) dynamics
$\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u$, however the computation
of $H^x$ and $H^u$ requires solving a nonlinear integral. Suppose that

@@

sets, we have extremal values of $H^x$ and $H^u$, i.e.

@@

\begin{equation}\label{eq:definition:element:wise:constraints:on:nonlinearities}
\mathcal V(x,u)=\left\{v:\min_k\{
H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge\right. \\ \left.v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}, \, i =1,\dots,n\right\}.

@@

is compact, since $\mathcal Z^\infty\vert_{(\hat\alpha,\hat\theta)}$ is compact and there exists a maximal $\theta_{\max}$
such that $\Lambda^{1,x}x+\Lambda^{1,\alpha}\hat\alpha+\Lambda^{1,\theta}\theta\leq\lambda^1$ can be satisfied
analogue there is a minimal $\theta_{\min}$. We can solve the optimisation programs

>>>>

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\biggl(\bigoplus_{i\leq k-1} 
\Psi^i\mathcal V(\mathcal X_k)\biggr)}_{=\mathcal S_2}.

@@

$y$ and its first derivative $\dot y$ as the states, i.e. $x = (y,\dot
y)^T$. We find that any equilibrium has $\dot{y}=0$ and
$u=\sqrt{\frac{gm}{c}} y$ for any positive position $y>0$.
Linearising the nonlinear differential equation $\dot x = f(x,u)$
around an equilibrium point $(\hat x, \hat u)$ 
%such that $f(\hat x,\hat u) = 0$, 
gives the approximate model 

@@

	 \dot{\tilde{x}} \approx \underbrace{\left(\begin{array}{cc}

@@

	\end{array}\right)}_{\frac{\partial f}{\partial x}(\hat x,\hat
      u)}\tilde x 
+ \underbrace{\left(\begin{array}{c}

@@

	\end{array}\right)}_{\frac{\partial f}{\partial u}(\hat x,\hat
      u)}\tilde u

@@

where $\tilde{x} = x-\hat{x}$, $\tilde{u} = u -\hat{u}$.
We derive the discrete time dynamics with sampling rate $T_s$ using
the Euler formula $x^+=x+T_s f(x,u) =:\tilde f(x,u)$ giving
\tilde{x}^+ \approx A \tilde{x} + B \tilde{u}, \quad
\Biggl\{\begin{aligned} A &= I+T_s\frac{\partial f}{\partial  x}(\hat
  x,\hat u) \\
B &= T_s \frac{\partial f}{\partial u}(\hat x,\hat u)
\end{aligned}
Although this system has a control input, the algorithm for computing the
MRPI set is applicable since we consider the closed loop system under
linear feedback  $u=Kx$, where $K$ satisfies the robust Lyapunov condition $V(x)-V((A+BK)x+Dw)\leq \gamma^2w^Tw$ with $V(x)=x^T P x\geq0$, i.e.
$x^TPx - ((A+BK)x+Dw)^TP((A+BK)x+Dw)\geq x^T(Q+K^TRK)x -\gamma^2 w^Tw$
for a minimum  $\gamma^2$, see e.g.~\cite{Boyd:94}.
A representation of disturbances acting on the linearised
model due to linearisation errors can be obtained using the
Mean Value Theorem for vector-valued functions (e.g.~\cite{Apostol:1974}).

@@

Let $g : \mathcal X \rightarrow\mathbb R^m$ be continuously
differentiable, $\mathcal X\subset\mathbb R^n$ be open,
and $x \in\mathcal X$, $h \in\mathbb R^n$ be such that 
$x + th \in\mathcal X$ for all $t\in [0 ,1]$. Then

@@

Using the Mean Value Theorem
and the linearisation around $(\hat{x},\hat{u})$, we obtain the successor state:

@@

x^+ &= \tilde{f}(\hat{x} + \tilde{x},\hat{u} + \tilde{u}) 
\\
&= \tilde f(\hat x, \hat u) 
+ \int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,
\hat u + t\tilde u) dt \cdot \tilde x  \\
&\quad + \int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u+
t\tilde u) dt\cdot \tilde u \\
%+ A \tilde x + B \tilde u - A \tilde x - B\tilde u\\
\Leftrightarrow 
\tilde x^+ &= A\tilde{x} + B \tilde{u} +\Bigl(
\int_0^1\frac{\partial\tilde f}{\partial x}(\hat x + t\tilde x,\hat u
             + t\tilde u)dt - A \Bigr)\tilde x 
\\ 
&\quad +\Bigl(\int_0^1\frac{\partial\tilde f}{\partial u}(\hat x + t\tilde x,\hat u + t\tilde u)dt - B\Bigr)\tilde u

@@

This implies the dynamics
\tilde x^+ = A\tilde x+B\tilde u + H^x\tilde x + H^u \tilde u, 
$H^x$ and $H^u$ can be determined by integration. Suppose that

@@

sets, the values of $H^x$ and $H^u$ are known, i.e.\

@@

\begin{multline}\label{eq:definition:element:wise:constraints:on:nonlinearities}
\mathcal V(x,u)=\biggl\{v:\min_k\{
H^x_{k,i}x+H^u_{k,i}u\}\leq v_i\,\wedge 
\\ 
v_i \leq \max_k\{H^x_{k,i}x+H^u_{k,i}u\}, \, i =1,\dots,n\biggr\}.
\end{multline}

@@

is compact, and since $\mathcal Z^\infty\vert_{(\hat\alpha,\hat\theta)}$
is compact, there exist a maximal $\theta_{\max}$ and likewise a minimal $\theta_{\min}$
such that $\Lambda^{1,x}x+\Lambda^{1,\alpha}\hat\alpha+\Lambda^{1,\theta}\theta\leq\lambda^1$ can be satisfied. We can solve the optimisation programs
